Automated topic naming to support analysis of software maintenance activities

### 2010-08-20 icse/icse2011.tex
edit summary of techniques

\subsection{Summary of techniques}
While unsupervised techniques (LSI and LDA are both unsupervised) are appealing in their lack of human intervention, and thus lower effort, supervised learners have the advantage of domain knowledge which typically means improved results. Our manual annotations were fairly quick to do, taking on average five minutes per 30 day period.

@@

We found that the multi-label learners of BR, CLR and HOMER did not do as well for Macro-ROC as NaiveBayes and other NaiveBayes derived learners. 
This suggests that by sticking together multiple NaiveBayes learners we could probably label sets of topics effectively, but it would require a separate NaiveBayes learner per label.

@@

\textbf{Understanding the figures} -- For example, in Fig. \ref{fig:mysql-timeline}, we see that the NFRs \emph{functionality}, \emph{portability} and \emph{maintainability} contain more labeled topics, since these NFRs have been more intensely shaded. % boxes. not sure boxes is important..
%We note that the gap in the MaxDB data is due to an interruption in the source data, having to do with the infrastructure for releasing developer artifacts, rather than specific occurrences in the project.
% I grepped query1.mrs2 http://softwareprocess.es/y/y/maxdb-76.tar.gz
% and                   http://softwareprocess.es/y/maxdb-7500.tar.gz
The gap in the MaxDB is due to the fact that other versions of MaxDB exist on different repositories and during this period from February 2005 to Jun 2005 the focus of development shifted to MaxDB 7.6. 
Immediately after this period of inactivity, there was a large deluge of commits added to the MaxDB 7.500 repositories.
%\todo[inline]{can I pin this down more ?}
There are more \textsf{None} labels in MaxDB because a number of topics were to do with code cleanup or automated checking using tools like \texttt{sutcheck}, a tool-specific to the development process at MaxDB.

\textbf{Timeline of key events} -- Figs. \ref{} show key events for each of our projects. Several external events (external to `normal' development activity, that is) affected our projects. For example, both projects show a high number of NFRs recognized at the first period of analysis. This is due to our window choice: we deliberately targeted our analysis to 
MySQL 3.23 First announced Major update \& End-of life
MaxDB 7.500 First announced

@@

\todo[inline]{try to pin down these reasons below}
%  MySQL 3.23 was put on maintenance.
% 
% MySQL forks repositories per every version and 3.23 was supported for a
% long time. there was 4.0 4.1 5.0 5.1
% 
% This is the MySQL 3.23 branch
% 
% Same thing with MaxDB 7.5
% 7.6 is in a different repository

>>>>

\subsection{Summary of techniques}
While unsupervised techniques (LSI and LDA are both unsupervised) are appealing in their lack of human intervention, and thus lower effort, supervised learners have the advantage of domain knowledge (training sets) which typically means improved results. 
Our manual annotations were fairly quick to do, taking on average five minutes per 30 day period.

@@

We found that the multi-label learners of BR, CLR and HOMER did not do as well for Macro-ROC as NaiveBayes and other naive Bayes derived learners. 
This suggests that by combining together multiple NaiveBayes learners we could probably label sets of topics effectively, but it would require a separate NaiveBayes learner per label.

@@

\textbf{Understanding the figures} -- For example, in Figure \ref{fig:mysql-timeline}, we see that the NFRs \emph{functionality}, \emph{portability} and \emph{maintainability} contain more labeled topics, since these NFRs have been more intensely shaded. % boxes. not sure boxes is important..
%We note that the gap in the MaxDB data is due to an interruption in the source data, having to do with the infrastructure for releasing developer artifacts, rather than specific occurrences in the project.
% I grepped query1.mrs2 http://softwareprocess.es/y/y/maxdb-76.tar.gz
% and                   http://softwareprocess.es/y/maxdb-7500.tar.gz
The gap in the MaxDB is due to the fact that other versions of MaxDB exist on different repositories and during this period from February 2005 to Jun 2005 the focus of development shifted to MaxDB 7.6. 
Immediately after this period of inactivity, there was a large deluge of commits added to the MaxDB 7.500 repositories.
%\todo[inline]{can I pin this down more ?}
There are more \textsf{None} labels in MaxDB because a number of topics were to do with code cleanup or automated checking using tools like \texttt{sutcheck}, a tool-specific to the development process at MaxDB.

%XXX 
\textbf{Timeline of key events} -- Figs. \ref{} show key events for each of our projects.  % where's the figure?
Several external events (external to `normal' development activity, that is) affected our projects. 
For example, both projects show a high number of NFRs recognized at the first period of analysis. 
This is due to our window choice: we deliberately targeted our analysis to 
when MySQL 3.23 was first announced %Major update \& End-of life
and when MaxDB 7.500 was first announced.

@@

%\todo[inline]{try to pin down these reasons below}
%  MySQL 3.23 was put on maintenance.
% 
% MySQL forks repositories per every version and 3.23 was supported for a
% long time. there was 4.0 4.1 5.0 5.1
% 
% This is the MySQL 3.23 branch
% 
% Same thing with MaxDB 7.5
% 7.6 is in a different repository
